%!TEX root = ../Thesis.tex
\section{Step 2}
The software spin uses Promela models to verify a concurrent model. The model shows rather the processes use variables and other shared data in a valid way. The processes should not be allowed to enter more than 4 cars at a time and only in one direction for our project.
\\

\subsection{Analysis}
The Promela code is a little different to get to work than the java code. The semaphore described previously result in the code found in appendix \ref{sec:jSpin}. The code display the enter part followed by the leave part of the cars alley class in java. The result of the analysis shows with 8 threads the program runs correctly. 

\begin{lstlisting}
pan: resizing hashtable to -w29.. pan: out of memory
hint: to reduce memory, recompile with
  -DCOLLAPSE # good, fast compression, or
  -DMA=84   # better/slower compression, or
  -DHC # hash-compaction, approximation
  -DBITSTATE # supertrace, approximation
(Spin Version 6.1.0 -- 4 May 2011)
Warning: Search not completed
	+ Partial Order Reduction
Full statespace search for:
	never claim         	- (none specified)
	assertion violations	+
	cycle checks       	- (disabled by -DSAFETY)
	invalid end states	+
State-vector 84 byte, depth reached 108, ... errors: 0 ...
 2.69e+08 states, stored
6.5625499e+08 states, matched
9.2525499e+08 transitions (= stored+matched)
1.4695379e+08 atomic steps
hash conflicts: 4.0118364e+08 (resolved)
Stats on memory usage (in Megabytes):
28732.300	equivalent memory usage for 
states (stored*(State-vector + overhead))
11478.569	actual memory usage for states 
    (compression: 39.95%)
         	state-vector as stored = 17 byte + 
         	    28 byte overhead
 4096.000	memory used for hash table (-w29)
    0.107	memory used for DFS stack (-m2000)
    4.417	memory lost to fragmentation
15570.259	total actual memory usage
pan: elapsed time 1.49e+03 seconds
pan: rate    180388 states/second
\end{lstlisting}

The analysis does not show any errors, but a warning is given "Search not complete". Other analysis have been run, which does not show the warning, but these are with less processes. These analysis can be found in the appendix \ref{sec:jSpin}. The problem is that the pan runs out of memory on the thin clients, which result in a termination. The program does the analysis, but takes a long time and the maksimum of processes running without the warning was 5. For 5 processes the analysis does seem to work every time, but does only have 1 car in the one direction and 4 in the other.

The analysis shows no errors which means the checks (found at the bottom of the code) do hold. The different semaphores are kept within the limits of the variables. 

\subsection{Implementation}
The code in appendix \ref{sec:jSpin} is a close implementation of the code in java, which can be found in appendix \ref{sec:alley}.
\\

Some of the challenges has been to get the jSpin code to do the exact same as the java code, but we have received some help from the TA to get it right. The challenges were to make the wait function along with the semaphore code to behave as intended. 

The semaphore was made with inlines for the P and V function. The inline is similar to methods and is easy to use within the project. The P function is done atomic and decrements the specific semaphore value by 1. The reason for begin atomic is to do the entire inline before another process can access the inline. For the V function the semaphore is simply incremented by 1.